### 2018-02-24 publications.tex
Added Osaka, AAS presentations.
Update publication. Science paper ApJ submitted.

\begin{benumerate}{6}
\item \textit{Modeling Radiative Feedback from Massive Stars: I.
  Implementation of Adaptive Ray Tracing Method and Tests}\\
\textbf{Kim, J.-G.}, Kim, W.-T., Ostriker, E. C.,\& Skinner A. M.
2017, ApJ, 851, 93
\item \textit{Disruption of Molecular Clouds by Expansion of Dusty H II
  Regions}\\
\textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
137
\item \textit{Instability of Magnetized Ionization Fronts
  Surrounding H II regions}\\
\textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
\item \textit{Nature of Wiggle Instability of Galactic Spiral
  Shocks}\\
Kim, W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
\item \textit{Instability of Evaporation Fronts in the
  Interstellar Medium}\\
\textbf{Kim, J.-G.}, Kim, W.-T. 2013, ApJ, 779, 48
\item \textit{Gravitational Instability of Rotating,
    Pressure-Confined,
    Polytropic Gas Disks with Vertical Stratification}\\
  \textbf{Kim, J.-G.}, Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012,
  ApJ, 761, 131
\end{benumerate}

\subsection{Papers in Preparation}
\begin{enumerate}
\item[] \textit{Modeling Radiative Feedback from Massive Stars: II.
    Dispersal of Giant Molecular Clouds by Photoionization and
    Radiation Pressure} \\
  \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, \textit{in
    prep}
\item[] \textit{Modeling Radiative Feedback from Massive Stars: III.
    Escape of Radiation} \\
  \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, \textit{in
    prep}
% \item[] \textit{Modeling Radiative Feedback from Massive Stars:
%     IV. Comparison of Star Formation Efficiencies in Observed and
%     Simulated Giant Molecular Clouds}\\
%   \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. \textit{2018, in
%     prep}
% \item[] \textit{Heating and Ionization of
%       the Diffuse Interstellar Medium by UV Radiation in TIGRESS}\\
%     \textbf{Kim, J.-G.}, Kim, C.-G., Seon K.-I., Ostriker, E. C., \&
%     Kim, W.-T. \textit{2018, in prep}
\end{enumerate}

>>>>

\begin{benumerate}{7}
\item \textit{Modeling Radiative Feedback from Massive Stars: II.
    Dispersal of Star-Forming Giant Molecular Clouds by
    Photoionization and Radiation Pressure} \\
  \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018,
  \textit{submitted to ApJ}
\item \textit{Modeling Radiative Feedback from Massive Stars: I.
  Implementation of Adaptive Ray Tracing Method and Tests}\\
\textbf{Kim, J.-G.}, Kim, W.-T., Ostriker, E. C.,\& Skinner A. M.
2017, ApJ, 851, 93
\item \textit{Disruption of Molecular Clouds by Expansion of Dusty H II
  Regions}\\
\textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
137
\item \textit{Instability of Magnetized Ionization Fronts
  Surrounding H II regions}\\
\textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
\item \textit{Nature of Wiggle Instability of Galactic Spiral
  Shocks}\\
Kim, W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
\item \textit{Instability of Evaporation Fronts in the
  Interstellar Medium}\\
\textbf{Kim, J.-G.}, Kim, W.-T. 2013, ApJ, 779, 48
\item \textit{Gravitational Instability of Rotating,
    Pressure-Confined,
    Polytropic Gas Disks with Vertical Stratification} \\
  \textbf{Kim, J.-G.}, Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012,
  ApJ, 761, 131
\end{benumerate}

\subsection{Papers in Preparation}
\begin{enumerate}
\item[] \textit{Modeling Radiative Feedback from Massive Stars: III.
    Escape of Ionizing and Non-ionizing Radiation from Star-Forming
    Giant Molecular Clouds} \\
  \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, \textit{in
    prep}
% \item[] \textit{Modeling Radiative Feedback from Massive Stars:
%     IV. Comparison of Star Formation Efficiencies in Observed and
%     Simulated Giant Molecular Clouds}\\
%   \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. \textit{2018, in
%     prep}
%   \item[] \textit{Heating and Ionization of
%     the Diffuse Interstellar Medium by UV Radiation in TIGRESS}\\
%     \textbf{Kim, J.-G.}, Kim, C.-G., Seon K.-I., Ostriker, E. C., \&
%     Kim, W.-T. \textit{2018, in prep}
\end{enumerate}
